Manuscript

### 2025-04-10 analysis/primary_analyses.qmd
add draft for table2

```{r}
# Funktion zum Extrahieren standardisierter Ladungen (nur einmal definieren)
get_std_loadings <- function(fit, model_name) {
  standardizedSolution(fit) %>%
    filter(op == "=~") %>%
    select(lhs, rhs, est.std) %>%
    mutate(model = model_name)
}

# ---- Alter ----
loadings1 <- get_std_loadings(fit1A6P, "age 1")
loadings2 <- get_std_loadings(fit1A2P, "age d1")
all_loadings12 <- bind_rows(loadings1, loadings2)

table_loadings12 <- all_loadings12 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings12)

# ---- Größe ----
loadings3 <- get_std_loadings(fit1G6P, "height 2")
loadings4 <- get_std_loadings(fit1G2P, "height d2")
all_loadings34 <- bind_rows(loadings3, loadings4)

table_loadings34 <- all_loadings34 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings34)

# ---- Gewicht ----
loadings5 <- get_std_loadings(fit1Ge6P, "weight 3")
loadings6 <- get_std_loadings(fit1Ge2P, "weight d3")
all_loadings56 <- bind_rows(loadings5, loadings6)

table_loadings56 <- all_loadings56 %>%
  pivot_wider(names_from = model, values_from = est.std)

print(table_loadings56)
```

@@

```{r}
bifac_df <- 
  bind_rows(
    standardizedSolution(fit1A6_p, type = "std.all") |> mutate(measure = "age", categories = "6"),
    standardizedSolution(fit1A2_p, type = "std.all") |> mutate(measure = "age", categories = "2"),
    standardizedSolution(fit1G6_p, type = "std.all") |> mutate(measure = "height", categories = "6"),
    standardizedSolution(fit1G2_p, type = "std.all") |> mutate(measure = "height", categories = "2"),
    standardizedSolution(fit1Ge6_p, type = "std.all") |> mutate(measure = "weight", categories = "6"),
    standardizedSolution(fit1Ge2_p, type = "std.all") |> mutate(measure = "weight", categories = "2")) |>
  filter(
    (lhs %in% c("age", "height", "weight") & op == "=~") |
    (rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~")) |>
  mutate(
    cause = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ lhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ rhs),
    item_name = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ rhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ lhs
    )) |> 
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
         suffix = as.numeric(sub(".*_", "", item_name))) %>%
  # For each prefix group, assign new_num as the rank of suffix in sorted order 
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3))
```

```{r}
table3 <- bifac_df |> 
  select(item, cause, measure, categories, est_print) |> 
  pivot_wider(names_from = c(measure, cause), values_from = est_print) |>
  flextable::as_grouped_data(groups = "categories") |>
  flextable::as_flextable() |>
  flextable::add_header_row(values = c("age", "height", "weight"),
    colwidths = c(4, 3, 3)) |>
  flextable::set_header_labels(
    values = list(
      item = "Item",
      age_age = "LV", height_height = "LV", weight_weight = "LV",
      age_Alter_realW = "age",
      height_Koerpergroesse_realW = "height",
      weight_Koerpergewicht_realW = "weight",
      age_Geschlecht = "sex", height_Geschlecht = "sex", weight_Geschlecht = "sex")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table3
```

@@

```{r}
results <- saveRDS(
  object = list(
    table3 = table3, table4 = table4
    ), 
  file = "../results/results.rds"
)
```

>>>>

```{r}
load_df <- 
  bind_rows(
    standardizedSolution(fit1A6P, type = "std.all") |> mutate(measure = "age", categories = "6"),
    standardizedSolution(fit1A2P, type = "std.all") |> mutate(measure = "age", categories = "2"),
    standardizedSolution(fit1G6P, type = "std.all") |> mutate(measure = "height", categories = "6"),
    standardizedSolution(fit1G2P, type = "std.all") |> mutate(measure = "height", categories = "2"),
    standardizedSolution(fit1Ge6P, type = "std.all") |> mutate(measure = "weight", categories = "6"),
    standardizedSolution(fit1Ge2P, type = "std.all") |> mutate(measure = "weight", categories = "2")) |>
  filter(lhs == "f1" & op == "=~") |> 
  mutate(item_name = rhs) |>
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
    suffix = as.numeric(sub(".*_", "", item_name))) |>
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  mutate(item = replace_na(as.character(item), "Physical item")) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3)) |>
  select(item, measure, categories, est_print) |>
  pivot_wider(names_from = c(measure, categories), values_from = est_print)

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6P))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2P))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6P))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2P))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6P))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2P))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)

table2 <- rbind(
    load_df |> rename(Measure = item) |> mutate(group = "Items"),
    fit_df |> rename(Measure = statistic) |> mutate(group = "Fit")
  ) |> 
  group_by(group) |>
  flextable::as_grouped_data(groups = "group") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("Measure", "Age", "Height", "Weight"),
    colwidths = c(1, 2, 2, 2)) |>
  flextable::set_header_labels(
    values = list(
      Measure = "Categories",
      age_6 = "6", age_2 = "2", 
      height_6 = "6", height_2 = "2",
      weight_6 = "6", weight_2 = "2")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table2
```

@@

```{r}
bifac_df <- 
  bind_rows(
    standardizedSolution(fit1A6_p, type = "std.all") |> mutate(measure = "age", categories = "6"),
    standardizedSolution(fit1A2_p, type = "std.all") |> mutate(measure = "age", categories = "2"),
    standardizedSolution(fit1G6_p, type = "std.all") |> mutate(measure = "height", categories = "6"),
    standardizedSolution(fit1G2_p, type = "std.all") |> mutate(measure = "height", categories = "2"),
    standardizedSolution(fit1Ge6_p, type = "std.all") |> mutate(measure = "weight", categories = "6"),
    standardizedSolution(fit1Ge2_p, type = "std.all") |> mutate(measure = "weight", categories = "2")) |>
  filter(
    (lhs %in% c("age", "height", "weight") & op == "=~") |
    (rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~")) |>
  mutate(
    cause = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ lhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ rhs),
    item_name = case_when(
      lhs %in% c("age", "height", "weight") & op == "=~" ~ rhs,
      rhs %in% c("Alter_realW", "Koerpergroesse_realW", "Koerpergewicht_realW", "Geschlecht") & op == "~" ~ lhs
    )) |> 
  # Create new columns: prefix (everything before underscore) and suffix (the numeric part)
  mutate(prefix = sub("_.*", "", item_name),
    suffix = as.numeric(sub(".*_", "", item_name))) |>
  # For each prefix group, assign new_num as the rank of suffix in sorted order 
  group_by(prefix) |>
  mutate(item = match(suffix, sort(unique(suffix)))) |>
  ungroup() |>
  mutate(est_print = papaja::printnum(est.std, gt1 = FALSE, digits = 3))
```

```{r}
table3 <- bifac_df |> 
  select(item, cause, measure, categories, est_print) |> 
  pivot_wider(names_from = c(measure, cause), values_from = est_print) |>
  flextable::as_grouped_data(groups = "categories") |>
  flextable::as_flextable(hide_grouplabel = TRUE) |>
  flextable::add_header_row(values = c("age", "height", "weight"),
    colwidths = c(4, 3, 3)) |>
  flextable::set_header_labels(
    values = list(
      item = "Item",
      age_age = "LV", height_height = "LV", weight_weight = "LV",
      age_Alter_realW = "age",
      height_Koerpergroesse_realW = "height",
      weight_Koerpergewicht_realW = "weight",
      age_Geschlecht = "sex", height_Geschlecht = "sex", weight_Geschlecht = "sex")) |>
  flextable::align(i = 1, align = "center", part = "header") |>
  flextable::border(i = 2, j = 1, border.top = officer::fp_border(width = 0), part = "header") |>
  flextable::border(i = 1, j = 1, border.bottom = officer::fp_border(width = 0), part = "header") |>
  flextable::theme_apa() |>
  ftExtra::colformat_md()
table3
```

@@

```{r}
results <- saveRDS(
  object = list(
    table2 = table2, table3 = table3, table4 = table4
    ), 
  file = "../results/results.rds"
)
```

### 2025-04-10 manuscript.qmd
add draft for table2

```{r}
#| label: "table2"
```

>>>>

```{r}
#| label: "tbl-2"
#| tbl-cap: Standardized item loadings (correlations with the latent variable) for 6 and 2 response categories 
#| ft.align: left
#| disable-apaquarto-processing: false
#| apa-note: CFI = Comparative Fit Index (scaled). RMSEA = Root Mean Squared Error of Approximation (scaled). SRMR = Standardized Root Mean Residual. Scaled chi-square, scaled df, and scaled p-value are reported. Correlations with the latent variable higher as the self-reported physical item are printed in bold typeface.

results$table2
```

As we can see in @tbl-2 ...
